Accelerated convergence of convective simulations using boundary value problems

### 2018-02-14 tex/bvp_paper.tex
starts cleaning up experiment section

\section{Experiment}
\label{sec:experiment}
We adopt the Oberbeck-Boussinesq approximation.  Under this choice, the
fluid has constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
of thermal expansion ($\alpha$). The variables of the fluid that are evolved are the velocity,
$\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, the temperature $T = T_0 + T_1$, and the pressure, $P$.
The density of the fluid is a constant, $\rho_0$, except on the
term where the constant gravitational acceleration, $\bm{g} = - g\hat{z}$, acts in the vertical momentum equation, 
where $\rho = \rho_0(1  - \alpha T_1)$.  
Under these choices, the equations of motion are \cite{spiegel&veronis1960}
\begin{gather}
\DivU = 0, 
	\label{eqn:dim_incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
-\frac{1}{\rho_0}\grad P - g( 1 - \alpha T_1)\hat{z} + \nu\grad^2\bm{u}, 
	\label{eqn:dim_bouss_momentum}
\\
\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 T_1,
	\label{eqn:dim_bouss_energy}
\end{gather}
We non-dimensionalize these equations on the layer height ($L_z$),
the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
and the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
by these choices, one time unit is a freefall time ($L_z/v_{ff}$).
We further re-arrange the momentum equation by introducing a reduced kinematic pressure,
$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where the gravitational
potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$.
The nature of $P$ in \RB convection, as a
Lagrange multiplier,
allows the treatment of $\varpi$ as a linear variable.
We time evolve the equations in the form,
\begin{gather}
\DivU = 0, 
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega}
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1,
	\label{eqn:bouss_energy}
\end{gather}
where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity, and the temperature
has been decomposed as $T \equiv T_0 + T_1$ where $T_0$ is the initial temperature
profile. We find Eq. (\ref{eqn:bouss_momentum}) to
be slightly faster numerically than the standard form in Eq. (\ref{eqn:dim_bouss_momentum}).
The dimensionless control parameters are set by the Rayleigh and Prandtl numbers,
\begin{equation}
\mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
\text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\chi} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}.
\end{equation}
The dimensionless vertical extent of the domain is $z = [-1/2, 1/2]$, and at the top and bottom boundaries
we impose no-slip, impenetrable boundary conditions such that $u = v = w = 0$ at $z = \pm 1/2$.
At the lower boundary, we employ a fixed flux condition such that $\partial T_1 / \partial z = 0$
at $z = -1/2$, and we impose a fixed temperature condition of $T_1 = 0$ at $z = 1/2$. Both
horizontal directions are periodic, extending over a range $x, y = [0, \Gamma]$, where
the aspect ratio is $\Gamma = 2$. In our 2D cases, we only examine the $x$ and $z$ dimensions
and we set $v = \partial_y = 0$.

The chosen thermal boundary conditions at the upper and lower plates
determine key quantities of the evolved state.
Studies of incompressible, Boussinesq, \RB convection often
employ fixed temperature (Dirichlet) or fixed heat flux
(Neumann) boundary conditions at both plates.  
Dirichlet conditions represent plates of infinite conductivity,
whereas Neumann conditions model plates of finite conductivity.  
Both types of conditions
transport heat in the same manner \cite{johnston&doering2009},
at least when the upper and lower conditions are symmetric.
Studies of convection which aim to model
astrophysical systems such as stars often employ a mixture of these
two types of boundary conditions \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.  
The flux at the lower boundary is fixed, modeling
the constant energy generation of the stellar core, 
while the outer boundary condition is held at a fixed temperature,
modeling the stellar surface which must output the energy generated internally.
This setup is a useful model for understanding natural
systems, but simulations which employ these boundary conditions suffer from a long 
thermal relaxation as the atmosphere loses energy and approaches the adiabat chosen by the
Dirichlet condition.  We choose these mixed conditions in part to better understand them, and in
part because these conditions minimize the number of assumptions that must be made in
setting up the boundary value problem.  For this choice of boundary conditions, the
critical Ra is Ra$_{\text{crit}} = 1295.78$, and we will often speak in terms of the
supercriticality, $S = \text{Ra}/\text{Ra}_{\text{crit}}$.

\subsection{The Boundary Value Problem}
\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/time_trace.png}
\caption{Traces of system energies vs. time for a long thermal rundown (a) and BVP convergence
(b) are shown for $S = 10^{4 + 2/3}$.  The horizontal extent of the subplots is set
such that one simulation time unit takes up an equal amount of paper space in (a) and (b). Volume averaged
kinetic energy is shown in black, and the volume averaged temperature with the top value removed, is shown
in red.
The dashed vertical line on (a) represents the time at which averaging begins in the BVP solution in (b),
and the horizontal dashed lines show the equilibrium value of the energies. The blue vertical lines represent
the beginning of the time-averaging window.
(c) System fluxes early in the run (the orange highlights in (a)) are shown.  
Black is the sum of the flux, purple
is the convective flux, and red is the conductive flux.
(d) Fluxes in the converged rundown IVP compared to the converged BVP.  The sum of flux is shown in
black \& grey, the convective flux is shown in purple \& pink, and the conductive flux is shown in red \& orange.
(e) The differences between the BVP and rundown fluxes is shown.  While not in perfect agreement, 
the BVP fluxes deviate from the rundown fluxes by only a few percent of the total flux, and
are much closer to the converged state than the initial fluxes, as in (c).
\label{fig:time_trace} }
\end{figure}

It is reasonable to assume that convection will evolve the mean temperature profile that
drives it over the course of a thermal diffusion time, $t_\chi = \mathcal{P}^{-1}$. Thus, as Ra
increases, the timescale for achieving a thermally converged mean temperature profile becomes intractable.
This prohibitively long thermal timescale in an Initial Value Problem (IVP)
can be skipped by coupling the IVP with a simple Boundary Value Problem
(BVP) solve. By using information about the convecting dynamical state of an unconverged solution,
a BVP can be used to solve for the evolved system state.
A comparison of a simulation running for the thermal timescale, and another where a BVP is used
to fast-forward atmospheric evolution, are shown in Fig \ref{fig:time_trace}a\&b.

@@

In general, the BVP solve is completed in the following steps:
\begin{enumerate}
\item Run the convective IVP. Once the convection achieves a volume-averaged Re of $\sqrt{\text{Ra}/\text{Ra}_{\text{crit}}}$,
wait for 50 freefall time units.  
\item Start taking the averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$, waiting either
30 freefall time units or until the average profiles change by no more than 1 part in 1000 on a
given timestep, whichever is a more difficult criterion. This ensures that
the profiles being used in the BVP are steady and smooth, and that they sample the full behavior of the convection.
\item Construct $\angles{w T_1}_{\text{steady}}$, $\xi$, and $\angles{\bm{u}\times\bm{\omega}}_{\text{steady}}$
from the flux profiles.
\item Solve for $\angles{T_1}$ and \angles{\varpi} of the
evolved state.  Adjust the mean profiles in the IVP.
\item Multiply the velocity field and the fluctuations in $T_1$ about its horizontal average by $\sqrt{\xi}$ in the IVP. 
\item Continue running the IVP for freefall 50 time units to allow for the velocities to equilibrate to their new background state.
\item Repeat steps 2-6 to complete a second BVP and get closer to the right solution now that we
are far from the very unstable transient period.
\item Take averages for the amount of time specified for the given run in Appendix \ref{section:appendix_table}.
\end{enumerate}

\subsection{Numerics}
We utilize the 
Dedalus\footnote{\url{http://dedalus-project.org/}} 
pseudospectral framework \cite{burns&all2016} to time-evolve  
(\ref{eqn:incompressible})-(\ref{eqn:bouss_energy}) 
using an implicit-explicit (IMEX), third-order, four-step 
Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
The linear terms (on the LHS of the equations) are solved implicitly,
while the nonlinear terms (RHS) are explicitly solved.
The temperature field is decomposed as $T = T_0(z) + T_1(x, y, z, t)$
and the velocity is $\bm{u} = w\bm{\hat{z}} + u\bm{\hat{x}} + v\bm{\hat{y}}$.
In our 2D runs, $v = 0$.
Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal, periodic) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.

As initial conditions, we fill $T_1$ with
random white noise whose magnitude is $10^{-6}(\text{Ra Pr})^{-1/2}$.
This ensures that the initial perturbations are much smaller than the
evolved convective temperature perturbations, even at large Ra.
We filter this noise spectrum in coefficient space, 
such that only the lower 25\% of the coefficients
have power.

@@

\appendix
\section{Table of Runs}
\label{section:appendix_table}
\begin{center}
\begin{tabularx}{\textwidth}{ X X X X X X X X X}
\hline															
$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{rundown}}$	&	Nu$_{\text{BVP}}$	\\
\hline															
$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	128	&	$52.8$	&	100	&	(TBD)	&	(TBD)	\\
$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	128	&	$77.6$	&	100	&	--	&	--	\\
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	128	&	$114$	&	100	&	--	&	--	\\
$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	128	&	$167$	&	100	&	--	&	--	\\
$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	128	&	$245$	&	100	&	--	&	--	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	256	&	$360$	&	100	&	--	&	--	\\
$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	256	&	$528$	&	100	&	--	&	--	\\
$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	256	&	$776$	&	100	&	--	&	--	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	512	&	$1.14 \cdot 10^3$	&	200	&	--	&	--	\\
$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	512	&	$1.67 \cdot 10^3$	&	500	&	--	&	--	\\
$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	1024	&	$2.45 \cdot 10^3$	&	500	&	--	&	--	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	1024	&	$3.60 \cdot 10^3$	&	500	&	--	&	--	\\
$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	1024	&	$5.28 \cdot 10^3$	&	500	&	--	&	--	\\
$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	1024	&	$7.76 \cdot 10^3$	&	500	&	--	&	--	\\
$10^5$	&	$1.30 \cdot 10^8$	&	512	&	2048	&	$1.14 \cdot 10^4$	&	500	&	--	&	--	\\
$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	2048	&	$1.67 \cdot 10^4$	&	500	&	--	&	--	\\
$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	2048	&	$2.45 \cdot 10^4$	&	500	&	--	&	--	\\
$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	4096	&	$3.60 \cdot 10^4$	&	500	&	--	&	--	\\
\hline															
\end{tabularx}
\end{center}

>>>>

\section{Experiment}
\label{sec:experiment}
We study incompressible \RB convection under the Oberbeck-Boussinesq approximation,
such that our fluid
has a constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
of thermal expansion ($\alpha$). The density of the fluid is a constant, $\rho_0$, except on the
term where the constant gravitational acceleration, $\bm{g} = - g\hat{z}$, acts in the vertical momentum equation, 
where $\rho = \rho_0(1  - \alpha T_1)$.  
Under these constraints, the equations of motion are \cite{spiegel&veronis1960}
\begin{gather}
\DivU = 0, 
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
-\frac{1}{\rho_0}\grad P - g( 1 - \alpha T_1)\hat{z} + \nu\grad^2\bm{u}, 
	\label{eqn:dim_bouss_momentum}
\\
\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 T_1,
	\label{eqn:dim_bouss_energy}
\end{gather}
where $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$ is the velocity, 
$T = T_0 + T_1$ are the initial and fluctuating components of temperature, 
and $P$ is the pressure.
We non-dimensionalize these equations such that the dimensionless unit of
length is the layer height ($L_z$),
temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
and velocity is in units of the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
by these choices, one time unit is a freefall time ($L_z/v_{ff}$).
We introduce a reduced kinematic pressure,
$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where the gravitational
potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$. As $P$ is a
Langrange multiplier under the Oberbeck-Boussinesq approximation, $\varpi$
can be treated straightforwardly as a linear variable. 
In non-dimensional form, Eqns. \ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
are
\begin{gather}
\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega}
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1.
	\label{eqn:bouss_energy}
\end{gather}
where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters $\mathcal{P}$ and $\mathcal{R}$ 
are set by the Rayleigh and Prandtl numbers,
\begin{equation}
\mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
\text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}.
\end{equation}

We study 2D and 3D convection in which the domain is a cartesian box, 
whose dimensionless vertical extent is $z \in [-1/2, 1/2]$, 
and which is horizontally period with an extent of $x, y \in [0, \Gamma]$ where $\Gamma = 2$ is the aspect
ratio. 
In the 2D cases, we set $v = \partial_y = 0$.
We specify no-slip, impenetrable boundary conditions at both the top and
bottom boundary and we use mixed thermal boundary conditions, such that
\begin{equation}
u = v = w \, \, \text{at}\,\,z = \pm 1/2, \qquad T_1 = 0 \,\,\text{at}\,\, z=+1/2, \qquad
\frac{\partial T_1}{\partial z} = 0\,\,\text{at}\,\,z=-1/2.
\label{eqn:bcs}
\end{equation}
For this choice of boundary conditions, the critical value of Ra at which
the onset of convection occurs is Ra$_{\text{crit}} = 1295.78$, and the
supercriticality of a run is defined as $S \equiv \text{Ra}/\text{Ra}_{\text{crit}}$.
Studies of convection which aim to model
astrophysical systems such as stars often employ mixed thermal
boundary conditions \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017},
as we do here; however, our choice of thermal boundary conditions here
reflects the fact that the conditions in Eqn. \ref{eqn:bcs} are the simplest
to implement in the process of accelerated evolution (see section \ref{subsection:ae})
we study here.

We utilize the 
Dedalus\footnote{\url{http://dedalus-project.org/}} 
pseudospectral framework \cite{burns&all2016} to evolve  
Eqns. (\ref{eqn:incompressible}), (\ref{eqn:bouss_momentum}), \& (\ref{eqn:bouss_energy}) 
forward in time
using an implicit-explicit (IMEX), third-order, four-step 
Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
The linear terms (on the LHS of the equations) are solved implicitly,
while the nonlinear terms (RHS) are explicitly solved.
Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal, periodic) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.

As initial conditions, we fill $T_1$ with
random white noise whose magnitude is $10^{-6}\mathcal{P}$.
This ensures that the initial perturbations are much smaller than the
evolved convective temperature perturbations, even at large Ra.
We filter this noise spectrum in coefficient space, 
such that only the lower 25\% of the coefficients
have power.

\subsection{The method of accelerated evolution}
\label{subsection:ae}
Here we describe a method of Accelerated Evolution (AE), and compare it to Standard Evolution
(SE).
It is reasonable to assume that convection will evolve the mean temperature profile that
drives it over the course of a thermal diffusion time, $t_\chi = \mathcal{P}^{-1}$. Thus, as Ra
increases, the timescale for achieving a thermally converged mean temperature profile becomes intractable.
This prohibitively long thermal timescale in an Initial Value Problem (IVP)
can be skipped by coupling the IVP with a simple Boundary Value Problem
(BVP) solve. By using information about the convecting dynamical state of an unconverged solution,
a BVP can be used to solve for the evolved system state.
A comparison of a simulation running for the thermal timescale, and another where a BVP is used
to fast-forward atmospheric evolution, are shown in Fig \ref{fig:time_trace}a\&b.

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/time_trace.png}
\caption{Traces of system energies vs. time for a long thermal rundown (a) and BVP convergence
(b) are shown for $S = 10^{4 + 2/3}$.  The horizontal extent of the subplots is set
such that one simulation time unit takes up an equal amount of paper space in (a) and (b). Volume averaged
kinetic energy is shown in black, and the volume averaged temperature with the top value removed, is shown
in red.
The dashed vertical line on (a) represents the time at which averaging begins in the BVP solution in (b),
and the horizontal dashed lines show the equilibrium value of the energies. The blue vertical lines represent
the beginning of the time-averaging window.
(c) System fluxes early in the run (the orange highlights in (a)) are shown.  
Black is the sum of the flux, purple
is the convective flux, and red is the conductive flux.
(d) Fluxes in the converged rundown IVP compared to the converged BVP.  The sum of flux is shown in
black \& grey, the convective flux is shown in purple \& pink, and the conductive flux is shown in red \& orange.
(e) The differences between the BVP and rundown fluxes is shown.  While not in perfect agreement, 
the BVP fluxes deviate from the rundown fluxes by only a few percent of the total flux, and
are much closer to the converged state than the initial fluxes, as in (c).
\label{fig:time_trace} }
\end{figure}

@@

@@

\appendix
\section{Table of Runs}
\label{appendix:run_table}
\begin{center}
\begin{tabularx}{\textwidth}{ X X X X X X X X X}
\hline															
$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{rundown}}$	&	Nu$_{\text{BVP}}$	\\
\hline															
$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	128	&	$52.8$	&	100	&	(TBD)	&	(TBD)	\\
$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	128	&	$77.6$	&	100	&	--	&	--	\\
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	128	&	$114$	&	100	&	--	&	--	\\
$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	128	&	$167$	&	100	&	--	&	--	\\
$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	128	&	$245$	&	100	&	--	&	--	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	256	&	$360$	&	100	&	--	&	--	\\
$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	256	&	$528$	&	100	&	--	&	--	\\
$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	256	&	$776$	&	100	&	--	&	--	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	512	&	$1.14 \cdot 10^3$	&	200	&	--	&	--	\\
$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	512	&	$1.67 \cdot 10^3$	&	500	&	--	&	--	\\
$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	1024	&	$2.45 \cdot 10^3$	&	500	&	--	&	--	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	1024	&	$3.60 \cdot 10^3$	&	500	&	--	&	--	\\
$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	1024	&	$5.28 \cdot 10^3$	&	500	&	--	&	--	\\
$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	1024	&	$7.76 \cdot 10^3$	&	500	&	--	&	--	\\
$10^5$	&	$1.30 \cdot 10^8$	&	512	&	2048	&	$1.14 \cdot 10^4$	&	500	&	--	&	--	\\
$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	2048	&	$1.67 \cdot 10^4$	&	500	&	--	&	--	\\
$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	2048	&	$2.45 \cdot 10^4$	&	500	&	--	&	--	\\
$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	4096	&	$3.60 \cdot 10^4$	&	500	&	--	&	--	\\
\hline															
\end{tabularx}
\end{center}

\section{Accelerated Evolution Recipe}
\label{appendix:recipe}
In general, the BVP solve is completed in the following steps:
\begin{enumerate}
\item Run the convective IVP. Once the convection achieves a volume-averaged Re of $\sqrt{\text{Ra}/\text{Ra}_{\text{crit}}}$,
wait for 50 freefall time units.  
\item Start taking the averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$, waiting either
30 freefall time units or until the average profiles change by no more than 1 part in 1000 on a
given timestep, whichever is a more difficult criterion. This ensures that
the profiles being used in the BVP are steady and smooth, and that they sample the full behavior of the convection.
\item Construct $\angles{w T_1}_{\text{steady}}$, $\xi$, and $\angles{\bm{u}\times\bm{\omega}}_{\text{steady}}$
from the flux profiles.
\item Solve for $\angles{T_1}$ and \angles{\varpi} of the
evolved state.  Adjust the mean profiles in the IVP.
\item Multiply the velocity field and the fluctuations in $T_1$ about its horizontal average by $\sqrt{\xi}$ in the IVP. 
\item Continue running the IVP for freefall 50 time units to allow for the velocities to equilibrate to their new background state.
\item Repeat steps 2-6 to complete a second BVP and get closer to the right solution now that we
are far from the very unstable transient period.
\item Take averages for the amount of time specified for the given run in Appendix \ref{section:appendix_table}.
\end{enumerate}
